|

### 2021-12-24 paper/dcpo_demsupport.Rmd
drop SEM discussion

As an alternative way, a structural equation model (SEM) which incorporates measurement model and structural links between variables together can also account for bias caused by simultaneity between variables and measurement models.
However, SEM is a method to test the match between the model and the data, subject to confirmation bias due to the existing of competing theories which we have in the theory on democracy and public opinion, omitted variables, linear causal relationship assumption, the sensitivity to the estimator choice when both endogenous and endogenous are contaminated by measurement errors, among others [@Tomarken2005].

In contrast, MOC is flexible to accommodate not only various models but also multiple layers of uncertainty in both opinion estimates and substantive models [@Kastellec2015, 792] where the model and joint distribution of the error and all the variables in the model determine the bias introduced by measurement errors [@Bound2001, 3708].

@@

This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
As the use of latent variables grows more common, political scientists should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
Recent cross-national time-series measures of, for example, European policy ideology [developed in @Caughey2019], immigration mood and immigration concern [presented in @Claassen2022], and public gender egalitarianism [introduced in @Woo2022], make possible a host of previously infeasible analyses, but the resulting research cannot be considered robust if it does not also incorporate these measures' quantified uncertainty.

@@

During the replications of @Claassen2020a;@Claassen2020b, we found several miscoding across the original data.
For example, in @Claassen2020b that the author coded the option "Necesitamos un líder fuerte que no tenga que ser elegid" as "strong_lapop_2" for the question:

>>>>

@@

This points to the absolute necessity of incorporating measurement uncertainty into analyses that include latent variables.
As the use of latent variables grows more common, political scientists should be aware that these variables' concomitant measurement uncertainty cannot be neglected.
Recent cross-national time-series measures of, for example, policy ideology across Europe [developed in @Caughey2019], immigration attitudes in Europe [presented in @Claassen2022], and public gender egalitarianism worldwide [introduced in @Woo2022], make possible a host of previously infeasible analyses, but the resulting research cannot be considered robust if it does not also incorporate these measures' quantified uncertainty.

@@

During the replications of @Claassen2020a;@Claassen2020b, we found several miscoding across the original data.
For example, in @Claassen2020b that the author coded the option "necesitamos un líder fuerte que no tenga que ser eligido" as "strong_lapop_2" for the question:
